Implementation of an Open-Source modular mangetic field camera hardware for usage in Low-Field MRI Systems

### 2023-10-21 documentation/paper/main.tex
.

% mixture of sensors
% tablee with ranges
% digital only at the moment
\subsection{Sensor slice}

@@

\begin{figure}[htbp]
\centerline{\includegraphics[width=8cm]{magcam_sensor_module.png}}
\caption{Sensor Slice with eight TLV493d sensors}
\label{magcam_sensor_module_fig}
\end{figure}

The sensor slice shown in Figure \ref{anpmagcam_sensor_module_fig_fig} consists of 8 TLV493d sensors spaced 8mm apart on an 8mm x 64mm PCB.
To build a larger sensor array, the golf finger pads of the board can be soldered to other similar boards in a daisy chain configuration.

@@

In this way, an 8x8 sensor array can be built quickly, and the mechanical stability and alignment is ensured by the interconnection of the golf finger pads.

@@

\subsection{Automatic Sub-Sensor Detection}

@@

>>>>

% mixture of sensors
% tablee with ranges
% digital only at the moment

\subsection{Sensor slice}

@@

Since all of the digital sensors listed in \ref{implemented_sensors_fig} are connected via an I2C bus, they can be addressed via an individual address.
When using several identical sensors on one sensor slice, however, address collisions occur on the I2C bus. Some I2C devices offer the option of changing the address in hardware via the wiring of address inputs, but this requires a change in the hardware. 
In order to prevent this, an I2C multiplexer switch IC .was used here. Thus, in the current hardware version, up to eight identical sensors with the same address can be used per slice.

\begin{figure}[htbp]
\centerline{\includegraphics[width=8cm]{magcam_sensor_module.png}}
\caption{Sensor Slice with eight TLV493d sensors and readout electronics (STM32G031, PCF8574 and TCA9548)on the lieft side.}
\label{magcam_sensor_module_fig}
\end{figure}

The sensor slice shown in Figure \ref{anpmagcam_sensor_module_fig} consists of eight TLV493d sensors spaced 8mm apart on an 8mm x 64mm PCB.
To build a larger sensor array, the gold finger pads of the board can be soldered to other similar boards in a daisy chain configuration.

@@

In this way, an n*8x8 sensor array can be built quickly. The mechanical stability and alignment is ensured by the interconnection of the golf finger pads.

@@

\subsection{Automatic Sensor-Slice Detection}

@@

* currently limited by software to 50hz
* canbus speed limitations
* enable average algorithms between bus send to allow a higher readout rate.
